Patterns in Knowledge Production: Political Ruptures and Imperial Dynamics Shaping Public Discourse in Sweden and Finland, 1640–1828

### 2017-10-16 inst/examples/20170201-manuscript.Rmd
ok

p <- ggplot(df, aes(x = publication_decade, y = n,
       color = catalog, shape = catalog)) + 
       geom_point(size = 4) + 
       geom_line(size = 1) + 
       ylab("Places (n)") +
       xlab("Decade") +
       # scale_color_manual(values = c("blue", "darkgreen")) +
       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 2)) + 
       guides(linetype = "none") +
       guides(shape = guide_legend(title = "Catalog", reverse = TRUE),
              color = guide_legend(title = "Catalog", reverse = TRUE)) +              
       ggtitle("Unique publication places") +
       scale_color_stata() +
       theme(axis.ticks.length=unit(3, "mm"), axis.ticks=element_line(size = 1))

@@

brsy <- seq(0, 1e4, 2000)
p <- ggplot(df, aes(x = publication_decade, y = n,
                    shape = catalog,
		    color = catalog)) + 
       geom_point(size = 4) + 
       geom_line(size = 1) + 
       ylab("Title count (n)") +
       xlab("Decade") +
       #scale_color_manual(values = c("blue", "darkgreen")) +
       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 2)) +
       scale_y_continuous(breaks = brsy, labels = brsy) +
       guides(
         shape = guide_legend(title = "Catalog", reverse = TRUE),
         color = guide_legend(title = "Catalog", reverse = TRUE)	 
       ) +
       ggtitle("Title count") +
       scale_color_stata()
print(p)
```

@@

  p <- p + ggtitle(paste("Paper consumption (", catal, ")", sep = "")) +
         scale_x_continuous(breaks = brs,
	   labels = insert_minor(brs, 5, start = ifelse(catal == "Fennica", 1500, 1550))) + 
         scale_y_continuous(breaks = seq(0, max(df2$paper), 2e6), label = scientific_10)

@@

pics <- list()
brs <- seq(min(decade(df$publication_year)), max(decade(df$publication_year)), 10)
brsy <- seq(0, round(max(na.omit(df$title_length)), -1), 10)
for (catal in unique(df$catalog)) {
  pics[[catal]] <- ggplot(subset(df, catalog == catal),
       aes(x = publication_year, y = title_length)) +
       geom_point(aes(size = n)) +
       geom_smooth(color = cols[[catal]], fill = cols[[catal]]) +
       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5, start = century(min(brs)) + 50)) +
       scale_y_continuous(breaks = brsy, labels = insert_minor(brsy, 2), limits = c(0, max(na.omit(df$title_length)))) +
       ggtitle(paste("Median title length (", catal, ")", sep = "")) + 
       xlab("Decade") +
       ylab("Title length (words)")
}

@@

  theme_set(theme_bw(20))
  p <- ggplot(dff, aes(x = publication_decade, y = f)) +
     geom_bar(position = "stack", stat = "identity", color = "black",
       aes(fill = publication_place)) + 
     xlab("Decade") +
     scale_fill_stata() 
     if (varname == "n") {
       p <- p + ggtitle(paste("Title count (", catalogue, ")", sep = "")) + 
                ylab("Title count (%)") 
     }
     if (varname == "paper") {
       p <- p + ggtitle(paste("Paper (", catalogue, ")", sep = "")) +
                ylab("Paper (%)")        
     }
     if (varname == "publishers") {
       p <- p + ggtitle(paste("Publishers (", catalogue, ")", sep = "")) +
                       ylab("Publishers (%)")
     }     
  p <- p + guides(fill = guide_legend(title = "")) 
  p <- p + scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5, start = century(min(dff$publication_decade)) + 50))

@@

}
}
library(gridExtra)
grid.arrange(pics[[1]], pics[[2]], pics[[4]], pics[[5]], nrow = 2)
rm(pics)
```

@@

p <- ggplot(df,
       aes(fill = period, y = paper.per.title, x = publication_place)) + 
       geom_bar(stat = "identity", color = "black", position = "dodge") +
       #scale_x_discrete(labels = c("1757-1765", "1766-1774", "1775-1783")) +
       #scale_fill_manual(values = c("darkgreen", "darkgray"))
       #scale_fill_brewer(palette="Greys") +
       scale_fill_stata() +       
       guides(fill = guide_legend(title = "Period")) +
       ylab("Paper (sheets)") + xlab("") +
       ggtitle("Average paper consumption per title")

@@

  p <- p + geom_line(data = dfm, aes(x = date, y = Documents), col = "black")
  p <- p + geom_point(data = dfm, aes(x = date, y = Documents), col = "black")
  p <- p + scale_x_continuous(breaks=brs, labels = insert_minor(brs, 2))
  p <- p + scale_y_continuous(breaks=brsy, labels = brsy)  
  p <- p + ylab("Title count (n)")
  p <- p + xlab("Year")
  p <- p + ggtitle(paste("Title count (", catal, " ", minyear, "-", maxyear, ")", sep = ""))
  print(p)

@@

theme_set(theme_bw(20))
brs <- seq(min(npub$publication_decade), max(npub$publication_decade), 10)  
p <- ggplot(npub, aes(x = publication_decade, y = n)) +
       geom_bar(stat = "identity", position = "stack", color = "black",
       		    aes(fill = publication_place)) + 
       xlab("Decade") +
       ylab("Publishers (n)") +
       scale_fill_stata() +       
       guides(fill = guide_legend(reverse = FALSE, title = "")) +
       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 2)) +   
       ggtitle(paste("Publishers (", catal, ")", sep = ""))

@@

theme_set(theme_bw(20))
brs <- seq(min(npub$publication_decade), max(npub$publication_decade), 10)  
p <- ggplot(npub, aes(x = publication_decade, y = n)) +
       geom_bar(stat = "identity", position = "stack", color = "black",
       		    aes(fill = publication_place)) + 
       xlab("Decade") +
       ylab("Publishers (n)") +
       scale_fill_stata() +
       scale_x_continuous(breaks = brs,
           labels = insert_minor(brs, 2, start = min(npub$publication_decade))) + 
       guides(fill = guide_legend(reverse = FALSE, title = "")) +
       ggtitle(paste("Publishers (", catal, ")", sep = ""))

@@

@@

p <- ggplot(df, aes(x = publication_year, y = n)) +
     #geom_bar(stat = "identity") +
     geom_point() +
     geom_line(size = 1) +     
     ggtitle("") +
     scale_x_continuous(breaks = brs, labels = insert_minor(brs, 10, start = 1770)) +
     xlab("Year") +
     ylab("Title count (n)") +
     ggtitle(paste("Publications in Vaasa (", catalogue, ")", sep = ""))

@@

# TITLE COUNT
theme_set(theme_bw(20))
brs <- seq(min(df$publication_decade), max(df$publication_decade), 10)
p <- ggplot(npub, aes(x = publication_decade, y = publisher)) +
      geom_point(aes(size = n)) +
      scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5, start = century(min(brs)) + 50)) + 
      xlab("Decade") +
      ylab("") +
      guides(size = guide_legend(title = "Title count (n)")) +
      ggtitle(paste("Top publishers in ", place, " (", catalogue, ")", sep = ""))

@@

brs <- seq(min(df$publication_decade), max(df$publication_decade), 10)
labs <- brs; labs[!brs %in% df$publication_decade] <- ""
p <- ggplot(dfm, aes(x = publication_decade, y = titles_per_capita)) +
       geom_line(aes(color = publication_place), size = 1) +
       geom_point(aes(shape = publication_place, color = publication_place), size = 5) +
       xlab("Decade") +
       ylab("Title count per capita (n)") +
       scale_color_stata() +
       #scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5)) +
       scale_x_continuous(breaks = brs, labels = labs) +                    
       ggtitle("Title count per capita") +
       guides(shape = guide_legend(title = "Place")) +
       guides(color = guide_legend(title = "Place")) 
print(p)

@@

df <- bind_rows(df1, df2)
brs <- seq(min(df$publication_decade), max(df$publication_decade), 10)
brsy <- seq(0, round(max(df$n), -3), 1e3)
labs <- brs; labs[!brs %in% df$publication_decade] <- ""
p <- ggplot(df, aes(x = publication_decade, y = n)) +
       geom_line(aes(color = publication_place), size = 1) +
       geom_point(aes(color = publication_place, shape = publication_place), size = 5) +
       xlab("Decade") +
       ylab("Title count (n)") +
       ggtitle("Title count (absolute)") +
       #scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5)) +
       scale_x_continuous(breaks = brs, labels = labs) +
       scale_y_continuous(breaks = brsy, labels = insert_minor(brsy, 1)) +                                  
       guides(shape = guide_legend(title = "Place")) +
       guides(color = guide_legend(title = "Place")) +
       scale_color_stata()
print(p)
```

@@

df <- bind_rows(df1, df2)
brs <- seq(min(df$publication_decade), max(df$publication_decade), 10)
p <- ggplot(df, aes(x = publication_decade, y = paper)) +
       geom_line(aes(color = publication_place), size = 1) +
       geom_point(aes(color = publication_place, shape = publication_place), size = 5) +
       xlab("Decade") +
       ylab("Paper (sheets)") +
       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5, start = century(min(brs)) + 50)) +
       scale_y_continuous(label = scientific_10) +
       ggtitle("Paper consumption (Octavo)") +
       guides(shape = guide_legend(title = "Place"), color = guide_legend(title = "Place")) +
       scale_color_stata()
print(p)
```

@@

brs <- seq(min(df$publication_decade), max(df$publication_decade), 10)
p <- ggplot(df, aes(x = publication_decade, y = mean_title_length)) +
       geom_bar(color = "black",
         aes(fill = publication_place), position = "dodge", stat = "identity") +
       xlab("Decade") +
       ylab("Title length (words)") +
       ggtitle("Average title length") +
       scale_fill_stata() +
       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5, start = century(min(brs)) + 50)) +
       guides(fill = guide_legend(title = "Place", reverse = TRUE))        
print(p)
```

@@

```{r Fig16, echo=FALSE, message=FALSE, warning=FALSE, fig.width=15, fig.height=7}
pics <- list()
theme_set(theme_bw(20))
myplaces <- c("Turku", "Greifswald", "Stockholm", "Uppsala", "Lund")

for (catalogue in c("Fennica", "Kungliga")) {

@@

   p <- ggplot(dfss,
      aes(x = publication_decade, y = f)) +
      geom_bar(position = "stack", stat = "identity",
      			aes(fill = language), color = "black") + 
      xlab("Decade") +
      ylab("Title count (%)") +
      ggtitle(paste(myplace, "/", catalogue)) +
      scale_fill_stata() +
      scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5)) +  
      #scale_fill_brewer(palette="Greys") +       
      guides(fill = guide_legend(title = "")) 
      #guides(fill = guide_legend(title = "")) +       
    pics[[paste(catalogue, myplace, sep = "-")]] <- p
  }
}

@@

p <- ggplot(df, aes(x = publication_decade, y = n, shape = language)) +
       geom_line(size = 1, aes(color = language)) +
       geom_point(size = 4, aes(color = language)) +
       scale_color_brewer(palette="Greys") +
       scale_fill_brewer(palette="Greys") +                     
       # geom_smooth(color = "black") +
       guides(shape = guide_legend(title = "Language"),
              color = guide_legend(title = "Language")) +
       scale_color_stata() +
       # scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5)) +
       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 2, start = century(min(brs)) + 40)) +                 
       ylab("Subject topics (n)") +
       xlab("Decade") +
       ggtitle(paste("Topic richness (", catalogue, ")", sep = ""))

@@

  # PAPER CONSUMPTION
  p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
       geom_point(aes(shape = language, color = language), size = 5) +
        geom_line(aes(color = language), size = 1) +       
       xlab("Decade") +
       ylab("Paper (sheets)") +
       guides(shape = guide_legend(title = "Language"),
              color = guide_legend(title = "Language")) +
       #scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5)) +
       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5, start = 1600)) +
       scale_y_continuous(label = scientific_10) + 
       scale_color_stata() +
       ggtitle(paste("Temporary sermons (", catalogue, ")", sep = ""))
  print(p)
```

@@

# PAPER CONSUMPTION
theme_set(theme_bw(20))
brs <- seq(min(df$publication_decade), max(df$publication_decade), 10)
p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
       geom_point(aes(shape = language, color = language), size = 5) +
       geom_line(aes(color = language), size = 1) +       
       xlab("Decade") +
       ylab("Paper (sheets)") +
       guides(shape = guide_legend(title = "Language"), color = guide_legend(title = "Language")) +
       scale_color_stata() +
       # scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5)) +
       #scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5, start = century(min(brs)) + 50)) +
       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 2)) +       
       scale_y_continuous(label = scientific_10) + 
       ggtitle(paste("Devotional literature (", catalogue, ")", sep = ""))

>>>>

p <- ggplot(df, aes(x = publication_decade, y = n,
       color = catalog, shape = catalog)) + 
       geom_point(size = 4) + 
       geom_line(size = 1) + 
       ylab("Places (n)") +
       xlab("Decade") +
       # scale_color_manual(values = c("blue", "darkgreen")) +
       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 2)) + 
       guides(linetype = "none") +
       guides(shape = guide_legend(title = "Catalog", reverse = TRUE),
              color = guide_legend(title = "Catalog", reverse = TRUE)) +              
       #ggtitl("Unique publication places") +
       ggtitle("Figure 1") +       
       scale_color_stata() +
       theme(axis.ticks.length=unit(3, "mm"), axis.ticks=element_line(size = 1))

@@

brsy <- seq(0, 1e4, 2000)
p <- ggplot(df, aes(x = publication_decade, y = n,
                    shape = catalog,
		    color = catalog)) + 
       geom_point(size = 4) + 
       geom_line(size = 1) + 
       ylab("Title count (n)") +
       xlab("Decade") +
       #scale_color_manual(values = c("blue", "darkgreen")) +
       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 2)) +
       scale_y_continuous(breaks = brsy, labels = brsy) +
       guides(
         shape = guide_legend(title = "Catalog", reverse = TRUE),
         color = guide_legend(title = "Catalog", reverse = TRUE)	 
       ) +
       #ggtitl("Title count") +
       ggtitle("Figure 2") +              
       scale_color_stata()
print(p)
```

@@

  p <- p + #ggtitl(paste("Paper consumption (", catal, ")", sep = "")) +
         ggtitle(paste("Figure 3", c("A", "B")[which(unique(df00$catalog) == catal)], sep = "")) +       
         scale_x_continuous(breaks = brs,
	   labels = insert_minor(brs, 5, start = ifelse(catal == "Fennica", 1500, 1550))) + 
         scale_y_continuous(breaks = seq(0, max(df2$paper), 2e6), label = scientific_10)

@@

pics <- list()
brs <- seq(min(decade(df$publication_year)), max(decade(df$publication_year)), 10)
brsy <- seq(0, round(max(na.omit(df$title_length)), -1), 10)
for (catal in unique(df$catalog)) {
  pics[[catal]] <- ggplot(subset(df, catalog == catal),
       aes(x = publication_year, y = title_length)) +
       geom_point(aes(size = n)) +
       geom_smooth(color = cols[[catal]], fill = cols[[catal]]) +
       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5, start = century(min(brs)) + 50)) +
       scale_y_continuous(breaks = brsy, labels = insert_minor(brsy, 2), limits = c(0, max(na.omit(df$title_length)))) +
       #ggtitl(paste("Median title length (", catal, ")", sep = "")) +
       ggtitle("Figure 4") +
       xlab("Decade") +
       ylab("Title length (words)")
}

@@

  theme_set(theme_bw(20))
  p <- ggplot(dff, aes(x = publication_decade, y = f)) +
     geom_bar(position = "stack", stat = "identity", color = "black",
       aes(fill = publication_place)) + 
     xlab("Decade") +
     scale_fill_stata() 
     if (varname == "n") {
       p <- p + #ggtitl(paste("Title count (", catalogue, ")", sep = "")) + 
                ylab("Title count (%)") 
     }
     if (varname == "paper") {
       p <- p + #ggtitl(paste("Paper (", catalogue, ")", sep = "")) +
                ylab("Paper (%)")        
     }
     if (varname == "publishers") {
       p <- p + #ggtitl(paste("Publishers (", catalogue, ")", sep = "")) +
                       ylab("Publishers (%)")
     }     
  p <- p + guides(fill = guide_legend(title = "")) 
  p <- p + scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5, start = century(min(dff$publication_decade)) + 50))

@@

}
}
library(gridExtra)
pics[[1]] <- pics[[1]] + ggtitle("Figure 5") 
grid.arrange(pics[[1]], pics[[2]], pics[[4]], pics[[5]], nrow = 2)
rm(pics)
```

@@

p <- ggplot(df,
       aes(fill = period, y = paper.per.title, x = publication_place)) + 
       geom_bar(stat = "identity", color = "black", position = "dodge") +
       #scale_x_discrete(labels = c("1757-1765", "1766-1774", "1775-1783")) +
       #scale_fill_manual(values = c("darkgreen", "darkgray"))
       #scale_fill_brewer(palette="Greys") +
       scale_fill_stata() +       
       guides(fill = guide_legend(title = "Period")) +
       ylab("Paper (sheets)") + xlab("") +
       ggtitle("Figure 6") 
       #ggtitl("Average paper consumption per title")

@@

  p <- p + geom_line(data = dfm, aes(x = date, y = Documents), col = "black")
  p <- p + geom_point(data = dfm, aes(x = date, y = Documents), col = "black")
  p <- p + scale_x_continuous(breaks=brs, labels = insert_minor(brs, 2))
  p <- p + scale_y_continuous(breaks=brsy, labels = brsy)  
  p <- p + ylab("Title count (n)")
  p <- p + xlab("Year")
  p <- p + ggtitle("Figure 7")   
  #p <- p + #ggtitl(paste("Title count (", catal, " ", minyear, "-", maxyear, ")", sep = ""))
  print(p)

@@

theme_set(theme_bw(20))
brs <- seq(min(npub$publication_decade), max(npub$publication_decade), 10)  
p <- ggplot(npub, aes(x = publication_decade, y = n)) +
       geom_bar(stat = "identity", position = "stack", color = "black",
       		    aes(fill = publication_place)) + 
       xlab("Decade") +
       ylab("Publishers (n)") +
       scale_fill_stata() +       
       guides(fill = guide_legend(reverse = FALSE, title = "")) +
       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 2)) +
       ggtitle("Figure 8")
       #ggtitl(paste("Publishers (", catal, ")", sep = ""))

@@

theme_set(theme_bw(20))
brs <- seq(min(npub$publication_decade), max(npub$publication_decade), 10)  
p <- ggplot(npub, aes(x = publication_decade, y = n)) +
       geom_bar(stat = "identity", position = "stack", color = "black",
       		    aes(fill = publication_place)) + 
       xlab("Decade") +
       ylab("Publishers (n)") +
       scale_fill_stata() +
       scale_x_continuous(breaks = brs,
           labels = insert_minor(brs, 2, start = min(npub$publication_decade))) + 
       guides(fill = guide_legend(reverse = FALSE, title = "")) +
       ggtitle("Figure 9")       
       #ggtitl(paste("Publishers (", catal, ")", sep = ""))

@@

# Augment missing years with 0
missing.years <- setdiff(1750:1828, df$publication_year)
df <- rbind(df, data.frame(publication_year = missing.years, n = rep(0, length(missing.years))))
df <- df %>% arrange(publication_year)

@@

p <- ggplot(df, aes(x = publication_year, y = n)) +
     #geom_bar(stat = "identity") +
     geom_point() +
     geom_line(size = 1) +     
     scale_x_continuous(breaks = brs, labels = insert_minor(brs, 10, start = 1770)) +
     xlab("Year") +
     ylab("Title count (n)") +
     ggtitle("Figure 10")
     #ggtitle(paste("Publications in Vaasa (", catalogue, ")", sep = ""))

@@

# TITLE COUNT
theme_set(theme_bw(20))
brs <- seq(min(df$publication_decade), max(df$publication_decade), 10)
p <- ggplot(npub, aes(x = publication_decade, y = publisher)) +
      geom_point(aes(size = n)) +
      scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5, start = century(min(brs)) + 50)) + 
      xlab("Decade") +
      ylab("") +
      guides(size = guide_legend(title = "Title count (n)")) +
      #ggtitle("Figure 11")      
      #ggtitle(paste("Top publishers in ", place, " (", catalogue, ")", sep = ""))
      ggtitle(paste("Figure 11:", place, " (", catalogue, ")", sep = ""))

@@

brs <- seq(min(df$publication_decade), max(df$publication_decade), 10)
labs <- brs; labs[!brs %in% df$publication_decade] <- ""
p <- ggplot(dfm, aes(x = publication_decade, y = titles_per_capita)) +
       geom_line(aes(color = publication_place), size = 1) +
       geom_point(aes(shape = publication_place, color = publication_place), size = 5) +
       xlab("Decade") +
       ylab("Title count per capita (n)") +
       scale_color_stata() +
       #scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5)) +
       scale_x_continuous(breaks = brs, labels = labs) +                    
       #ggtitle("Title count per capita") +
       ggtitle("Figure 12") +       
       guides(shape = guide_legend(title = "Place")) +
       guides(color = guide_legend(title = "Place")) 
print(p)

@@

df <- bind_rows(df1, df2)
brs <- seq(min(df$publication_decade), max(df$publication_decade), 10)
brsy <- seq(0, round(max(df$n), -3), 1e3)
labs <- brs; labs[!brs %in% df$publication_decade] <- ""
p <- ggplot(df, aes(x = publication_decade, y = n)) +
       geom_line(aes(color = publication_place), size = 1) +
       geom_point(aes(color = publication_place, shape = publication_place), size = 5) +
       xlab("Decade") +
       ylab("Title count (n)") +
       #ggtitle("Title count (absolute)") +
       ggtitle("Figure 13") +              
       #scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5)) +
       scale_x_continuous(breaks = brs, labels = labs) +
       scale_y_continuous(breaks = brsy, labels = insert_minor(brsy, 1)) +                                  
       guides(shape = guide_legend(title = "Place")) +
       guides(color = guide_legend(title = "Place")) +
       scale_color_stata()
print(p)
```

@@

df <- bind_rows(df1, df2)
brs <- seq(min(df$publication_decade), max(df$publication_decade), 10)
p <- ggplot(df, aes(x = publication_decade, y = paper)) +
       geom_line(aes(color = publication_place), size = 1) +
       geom_point(aes(color = publication_place, shape = publication_place), size = 5) +
       xlab("Decade") +
       ylab("Paper (sheets)") +
       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5, start = century(min(brs)) + 50)) +
       scale_y_continuous(label = scientific_10) +
       #ggtitle("Paper consumption (Octavo)") +
       ggtitle("Figure 14") +                     
       guides(shape = guide_legend(title = "Place"), color = guide_legend(title = "Place")) +
       scale_color_stata()
print(p)
```

@@

brs <- seq(min(df$publication_decade), max(df$publication_decade), 10)
p <- ggplot(df, aes(x = publication_decade, y = mean_title_length)) +
       geom_bar(color = "black",
         aes(fill = publication_place), position = "dodge", stat = "identity") +
       xlab("Decade") +
       ylab("Title length (words)") +
       #ggtitle("Average title length") +
       ggtitle("Figure 15") +                            
       scale_fill_stata() +
       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5, start = century(min(brs)) + 50)) +
       guides(fill = guide_legend(title = "Place", reverse = TRUE))        
print(p)
```

@@

```{r Fig16, echo=FALSE, message=FALSE, warning=FALSE, fig.width=15, fig.height=7}
pics <- list()
theme_set(theme_bw(20))
myplaces <- c("Turku", "Greifswald", "Stockholm", "Uppsala", "Lund")
cnt <- 0
for (catalogue in c("Fennica", "Kungliga")) {

@@

   p <- ggplot(dfss,
      aes(x = publication_decade, y = f)) +
      geom_bar(position = "stack", stat = "identity",
      			aes(fill = language), color = "black") + 
      xlab("Decade") +
      ylab("Title count (%)") 
      #ggtitle(paste(myplace, "/", catalogue)) +
      if (cnt == 0) {
        p <- p + labs(title = "Figure 16")
	cnt <- 1
      }

      p <- p + labs(subtitle = paste(myplace, "/", catalogue)) +                 
      scale_fill_stata() +
      scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5)) +  
      #scale_fill_brewer(palette="Greys") +       
      guides(fill = guide_legend(title = "")) 
      #guides(fill = guide_legend(title = "")) +       
    pics[[paste(catalogue, myplace, sep = "-")]] <- p
  }
}

@@

p <- ggplot(df, aes(x = publication_decade, y = n, shape = language)) +
       geom_line(size = 1, aes(color = language)) +
       geom_point(size = 4, aes(color = language)) +
       scale_color_brewer(palette="Greys") +
       scale_fill_brewer(palette="Greys") +                     
       # geom_smooth(color = "black") +
       guides(shape = guide_legend(title = "Language"),
              color = guide_legend(title = "Language")) +
       scale_color_stata() +
       # scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5)) +
       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 2, start = century(min(brs)) + 40)) +                 
       ylab("Subject topics (n)") +
       xlab("Decade") +
       ggtitle("Figure 17")
       #ggtitle(paste("Topic richness (", catalogue, ")", sep = ""))

@@

  # PAPER CONSUMPTION
  p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
       geom_point(aes(shape = language, color = language), size = 5) +
        geom_line(aes(color = language), size = 1) +       
       xlab("Decade") +
       ylab("Paper (sheets)") +
       guides(shape = guide_legend(title = "Language"),
              color = guide_legend(title = "Language")) +
       #scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5)) +
       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5, start = 1600)) +
       scale_y_continuous(label = scientific_10) + 
       scale_color_stata() +
       ggtitle("Figure 18")
       #ggtitle(paste("Temporary sermons (", catalogue, ")", sep = ""))
  print(p)
```

@@

# PAPER CONSUMPTION
theme_set(theme_bw(20))
brs <- seq(min(df$publication_decade), max(df$publication_decade), 10)
p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
       geom_point(aes(shape = language, color = language), size = 5) +
       geom_line(aes(color = language), size = 1) +       
       xlab("Decade") +
       ylab("Paper (sheets)") +
       guides(shape = guide_legend(title = "Language"), color = guide_legend(title = "Language")) +
       scale_color_stata() +
       # scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5)) +
       #scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5, start = century(min(brs)) + 50)) +
       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 2)) +       
       scale_y_continuous(label = scientific_10) +
       ggtitle("Figure 19")       
       # ggtitle(paste("Devotional literature (", catalogue, ")", sep = ""))
